### 2014-04-08 brains-protocol.tex
Move figures around, and create one page of figures per feature
General cleanup of figures, adding a link to computed figures from the code
Rework up to 3.2.3 (excluded)

\begin{itemize}
    \item \rk{Add word frequency as a feature, and maybe link it to Kolmogorov's 5/3 law in turbulences}
    \item \textbf{Age of Acquisition}: the average age at which words are learned, obtained from~\citet{kuperman12},
    \item The average \textbf{Number of Phonemes} for all pronunciations of a word, obtained from the Carnegie Mellon University Pronouncing Dictionary~\citep{Weide98},\footnote{The CMU Pronouncing Dictionary is included in the NTLK package~\citep{Bird09}, the natural language processing toolkit we used for the analysis.}
    \item The average \textbf{Number of Syllables} for all pronunciations of a word, also obtained from the CMU Pronouncing Dictionary.
\end{itemize}

We also considered grammatical types within quotations by detection of \emph{Part-of-Speech} (POS) categories, using the Penn TreeBank Project typology~\citep{Santorini90} and thereby distinguishing verbs, nouns, adjectives and adverbs.
The results were however extremely similar across the various categories, exhibiting no specific effect of words belonging to different POS categories.

@@

Additional to classical psycholinguistic measures, we also considered more recently studied variables based on semantic network properties.
We relied on two types of network-based data: curated synonym associations provided by WordNet~\citep{WordNet10}, and ``free association'' norms collected by~\citet{Nelson04}.

The WordNet (WN) database gathers more than \num{117000} concepts and about \num{147000} words attached to these concepts.
WordNet entries are disambiguated words, called ``lemmas'', which are grouped into concepts called ``synsets'': all the lemmas in a synset are synonyms for the same single meaning.
Note that synsets also encode grammatical category, so the choice of a synset for a word (thus creating a lemma) immediately determines the grammatical category of that word.
Non-disambiguated words make the nodes of the semantic network we build (i.e. homograph lemmas are aggregated into a single node), and a node's neighbours are synonymous lemmas belonging to the same synset(s) as the lemma(s) represented by that node.
In other words, synsets induce cliques in the semantic network, and a word with several meanings belongs to as many cliques as it has meanings.
\TB{Links connecting two synonymous lemmas are assigned a weight corresponding to the number of times these lemmas are mentioned by WordNet as synonyms, i.e. in the same synset.}
\rk{We might spare ourselves that last sentence since we drop that aspect further down.}

Free Association (FA) norms record the words that come to mind when people are presented with a given cue (that is the ``free association'' task).
As \citeauthor{Nelson04} explain,
\begin{quote}
free association response probabilities index the likelihood that one word can cue another word to come to mind with minimal contextual constraints in effect.~\citep{Nelson04}
\end{quote}
Following \citet{Griffiths07}, we consider the directed weighed network formed by the association norms, that is the network where words are nodes and edges are directed from cue to associated word, with a weight equal to the probability of that target word being produced when this particular cue was presented.

While the original WN network is a weighted, undirected network, the FA network is a directed network where weights have a different meaning.
Both semantic networks describe synonymy relationships corresponding to qualitatively distinct forms of association: either from a linguistic viewpoint (WN) or from the perspective of actual information retrieval by humans (FA).
In  order to work in a unified framework, we shall consider links as an information on the existence of some sort of association between two words and transform both networks into undirected, unweighed networks.
\rk{Roll back to directed FA, and explain that it's a link between in-vivo spontaneous substitution and in-vitro forced substitution.
We could even add a more precise analysis using FA data directly (instead of features on the FA network), or keep that for the processual model.}

\bigskip
We introduce three standard network-based measures to be used on both the WN and FA networks:

\begin{itemize}
    \item \textbf{Distance} between two words, a classical dyadic network measure corresponding to the shortest path length between two nodes.
    This measure may be used as a proxy of the remoteness between two given words, which is likely to influence the likelihood of a word being a relevant substitution candidate for another word.
    \item \textbf{Centrality} $k$, measured by the number of neighbours of a given node, which can be interpreted as a proxy for the polysemy of words.
    \TB{For the directed network FA we also define the incoming centrality $k'$ (number of neighbours pointing \emph{to} that node)}.
    \rk{Rephrase once we rolled back FA to directed}
    Note that in the present case, there is a quasi-perfect correlation between node degree and node \emph{PageRank}~\citep{Page99}, which had already been used in~\citet{Griffiths07} and may be interpreted as a generalized and recursive measure of word polysemy: central nodes in the PageRank sense are those which are linked to many nodes themselves linked to many nodes, and so on recursively.
    \item \textbf{Clustering coefficient} $c$, which measures the extent to which a node belongs to a local aggregate of tightly connected nodes, and defined as the ratio between the number of actual v. possible edges between a node's neighbours \cite{watt-coll}.
    In the WN network, a word is likely to have a higher clustering coefficient whenever the synsets to which it belongs are themselves semantically linked.
    This measure had been used by \citet{Chan10}.
\end{itemize}

\TB{Betweenness coefficient, another measure of node centrality describing the extent to which a node tends to connect otherwise remote areas of the network~\citep{free:set}.
More technically, it corresponds to the normalized number of shortest paths connecting dyads which pass through that node; the higher the coefficient, the more important that node is in ensuring the connectedness of the rest of the network.
Correlation between FA-BC and FA-PR is $0.74$; between WN-BC and WN-PR it is $0.83$.}
\rk{We dropped this, right?}

@@

\begin{figure}[!th]
    \includegraphics[width=\linewidth]{algorithms/Rplot.pdf}
    \caption{Variable correlations \rk{rebuild with the variables we talk about and keep}}
\end{figure}

@@

\begin{figure*}[h]
    \centering
    \def\svgwidth{\textwidth}
    \small
    \input{images/model-slidetimebags-b.pdf_tex}
    \caption{Detection of substitutions according to model \rk{update text in figure}}
    \label{fig:model-slidetimebags}
\end{figure*}

>>>>

\begin{itemize}
    \item \textbf{Word frequency}: the frequency at which words appear in our dataset, \rk{add ref saying it's important}
    \item \textbf{Age of Acquisition}: the average age at which words are learned, obtained from~\citet{kuperman12},
    \item The average \textbf{Number of Phonemes} for all pronunciations of a word, obtained from the Carnegie Mellon University Pronouncing Dictionary~\citep{Weide98},\footnote{The CMU Pronouncing Dictionary is included in the NTLK package~\citep{Bird09}, the natural language processing toolkit we used for the analysis.}
    \item The average \textbf{Number of Syllables} for all pronunciations of a word, also obtained from the CMU Pronouncing Dictionary,
    \item The \textbf{Number of Meanings} for a word, obtained from WordNet~\citep{WordNet10}. \rk{add ref on why it's important}
\end{itemize}

We also considered grammatical types within quotations by detection of \emph{Part-of-Speech} (POS) categories, using the Penn TreeBank Project typology~\citep{Santorini90} and thereby distinguishing verbs, nouns, adjectives and adverbs.
The results were however extremely similar across the various categories, exhibiting no specific effect of words belonging to different POS categories.
\rk{See \#8 for this fact-check}

@@

Additional to classical psycholinguistic measures, we also considered more recently studied variables based on semantic network properties.
We relied on the ``free association'' norms collected by~\citet{Nelson04} which naturally embed information on the idea association process underlying transformation of quotations.

Free Association (FA) norms record the words that come to mind when people are presented with a given cue (that is the ``free association'' task).
As \citeauthor{Nelson04} explain,
\begin{quote}
free association response probabilities index the likelihood that one word can cue another word to come to mind with minimal contextual constraints in effect.~\citep{Nelson04}
\end{quote}
Following \citet{Griffiths07}, we first consider the directed weighed network formed by the association norms, that is the network where words are nodes and edges are directed from cue to associated word, with a weight equal to the probability of that target word being produced when this particular cue was presented.
\rk{we're in fact using the unweighed version of the network. Why?}
This network is of particular interest since it measures the \emph{in-vitro forced-choice} version of a substitution whereas the data we analyse is the \emph{in-vivo spontaneous} version of what we otherwise hypothesize to be the same process.

\bigskip
We introduce three standard network-based measures to be used on both the FA network \rk{adapt once the weighing question (\#8) is settled}:

\begin{itemize}
    \item \textbf{Centrality} $k$, measured by the number of incoming edges to a given node, i.e. the number of cues for which a given word is triggered as an association, which strongly relates to word polysemy.
    Note that in the present case, there is a quasi-perfect correlation between node incoming degree and node \emph{pagerank}~\citep{Page99}, a measure which had already been used by~\citet{Griffiths07} and which may be interpreted as a generalized and recursive measure of word polysemy: central nodes in the pagerank sense are words often selected as targets when presented with cues themselves often selected as targets, and so on recursively.
    \item \textbf{Clustering coefficient} $c$, which measures the extent to which a node belongs to a local aggregate of tightly connected nodes, and defined as the ratio between the number of actual v. possible edges between a node's neighbours \cite{watt-coll}.
    We compute the clustering coefficient on the undirected version of the FA network; we thus measure if a word belongs more or less to a local aggregate of equivalent words (from a ``free association'' point of view).
    \item \textbf{Betweenness coefficient} $b$, another measure of node centrality describing the extent to which a node tends to connect otherwise remote areas of the network~\citep{free:set}.
    More technically, it corresponds to the normalized number of shortest paths connecting dyads which pass through that node; the higher the coefficient, the more important that node is in ensuring the connectedness of the rest of the network.
    This quantity tells us if some words behave like unavoidable waypoints on the path associating one word to another.
\end{itemize}

@@

\begin{figure}[!th]
    \includegraphics[width=\linewidth]{images/computed-figures/feature_correlations-filter1.png}
    \caption{Variable correlations \rk{rebuild with the variables we talk about and keep}}
\end{figure}

@@

\rk{Add figure describing the chosen model}
